---
title: "DASC_Week_1"
output: html_document
---

```{r}
install.packages("tidyverse")
library(tidyverse)
```


# Task 1

## Code

```{r}
ggplot(data = mpg)
```

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = cyl, y = hwy))
```
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = class, y = drv))
```


## 3.2.4 Exercises

1. The graph above does not display anything, because it was not specified what is to be displayed. the ggplot() function allows you to add several layers, but there is no standard view that can be applied.

2. The mpg data pack has 234 rows and 11 columns.

3. The drv variable describes the type of drive train (front wheel / rear wheel / 4 wheel)

4. Displayed in the code section above.

5. Displayed in the code section above. This scatterplot is not useful because one of the axes displays a value that does not increase / decrease but can only be at 3 different positions. In order to make a useful diagram you would have to count how many of the cars actually share the same drive train in correlation to the car class.

# Task 2

## 3.3.1 Exercises

1. The first code is the wrong code, the second code section displays the correct code. The issue is that the colouring was added in the aes() block instead of the geom_point() function.

False code
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

```

Correct code
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```

2. The difference between continuous variables and categorical ones is that categorical variables can only be of a set of certain values, like the gender of a person, whereas continuous variables have a theoretically infinite range.

Categorical variables -> manufacturer, model, trans, drv, fl, class<br>
Continuous variables -> displ, year, cyl, cty, hwy

3. The large difference between mapping a continuous and a categorical variable to any aesthetic modifier is that a cetgegorical variable has harsh differences in the choice whereas the continuous modifier shows a "dropoff" in the changes.

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = class))
```

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = hwy))
```

# Task 3

1. The continuous variable is more or less converted into a categorical one. Meaning that there are a lot of facets that are being displayed.

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(~ cty)
```

2. The empty cells mean that there are simply no combinations recorded by the study. Since we have two categorical variables here this is quite likely that this might happen.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
```

3. The "." allows to vertically or horizontally realign the facets.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

4. The advantage of using faceting is that you can see a clearer grouping of the different car classes. What might happen is that you lose the overview of how they are settled in relation to the other ones. If you were to enhance the size of the dataset you would be able to see more irregular cases, meaning that the groupings would be much more spreaded out.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

# Task 4

1. Line chart: geom_line() / geom_smooth(), Boxplot: geom_boxplot(), Histogram: geom_histogram(), Area chart: geom_area()

2. I predicted the outcome as it was but I was missing out on the fact that the "(se = FALSE)" would eliminate the spread view.

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

3. I suspect that the legend of the shown diagram would be removed. Removing it would only reduce the ease with which the diagram could be read.

4. The "se" argument could add the range of tolerance on the values that are being smoothed out.
